\bf Is this normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-04 paper.qmd
Placeholder results for weather data

#preferred solution 5 clusters using dunn/dunn2 index
set.seed(150)
X_km <- kmeans(X_outside_scaled, 5)
# making a vector that labels all points
# use 0 to indicate point is not an outlier
cluster_labels_all <- as_tibble(X,
                               rownames = "year") %>%
  left_join(as_tibble(X_km$cluster,
                              rownames = "year")) %>%
  mutate(cluster = if_else(is.na(value), 0, value))
cluster_labels <- factor(cluster_labels_all$cluster,
                         levels = c(1:5, 0))

set.seed(22)
animate_xy(X, 
           guided_anomaly_tour(anomaly_index(),
                               ellipse=as.matrix(Sigma),
                               ellc = size_weather,
                               ellmu = mu), 
           ellipse=as.matrix(Sigma), ellc = size_weather,
           ellmu = mu,
           axes="off", col = as.factor(cluster_labels),
           palette = "Purple-Yellow",
           center = FALSE, rescale = FALSE)

@@

>>>>

#preferred solution 5 clusters using dunn/dunn2 index
set.seed(150)
X_km <- kmeans(X_outside_scaled, 5)
# making a vector that labels all points
# use 0 to indicate point is not an outlier
cluster_labels_all <- as_tibble(X,
                               rownames = "year") %>%
  left_join(as_tibble(X_km$cluster,
                              rownames = "year")) %>%
  mutate(cluster = if_else(is.na(value), 0, value)) %>%
  arrange(cluster)
cluster_labels <- factor(cluster_labels_all$cluster,
                         levels = c(1:5, 0))

X_sorted <- cluster_labels_all %>%
  select(-year, -cluster, -value)

set.seed(22)
animate_xy(as.matrix(X_sorted), 
           guided_anomaly_tour(anomaly_index(),
                               ellipse=as.matrix(Sigma),
                               ellc = size_weather,
                               ellmu = mu), 
           ellipse=as.matrix(Sigma), ellc = size_weather,
           ellmu = mu,
           axes="bottomleft",
           col = as.factor(cluster_labels),
           palette = "Purple-Yellow",
           center = FALSE, rescale = FALSE)

# color codes
# "#80146E" "#7262B2" "#31A0C2" "#5ECBBB" "#B9E5B9"
# "#F5F2D8"
# wait for getting random starting planes for
# better results
set.seed(55)
animate_xy(X_sorted[cluster_labels == 4,], 
           guided_anomaly_tour(anomaly_index(),
                               ellipse=as.matrix(Sigma),
                               ellc = size_weather,
                               ellmu = mu), 
           ellipse=as.matrix(Sigma), ellc = size_weather,
           ellmu = mu,
           axes="bottomleft",
           col = "#5ECBBB", half_range = 7,
           center = FALSE, rescale = FALSE)

@@

::: {#fig-weather layout-ncol=2}

![All outlying points.](images/weather1.png){#fig-weather1 width=300 align="center"}

![Only cluster 4.](images/weather2.png){#fig-weather2 width=300 align="center"}

Projection identified by the anomaly index. (a) shows the preferred projection when averaging all outlying points. (b) shows the preferred projection when optimizing only for cluster 4, which could not be resolved in the view in (a).
:::

### 2024-07-04 paper.tex
Placeholder results for weather data

>>>>

\includegraphics[width=3.125in,height=\textheight]{images/weather1.png}

\subcaption{\label{fig-weather1}All outlying points.}

\includegraphics[width=3.125in,height=\textheight]{images/weather2.png}

\subcaption{\label{fig-weather2}Only cluster 4.}

\caption{\label{fig-weather}Projection identified by the anomaly index.
(a) shows the preferred projection when averaging all outlying points.
(b) shows the preferred projection when optimizing only for cluster 4,
which could not be resolved in the view in (a).}
